\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2015-12-15 paper/paper.Rnw
Cleanup

<<setup, echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
library(lme4)
library(ggplot2)
library(mnormt)
library(tidyr)
# Convert reshape2 to tidyr, melt to gather - done
#library(reshape2)
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
library(stringr)
library(pander)
#library(splitstackshape) - changed cSplit to unnest
#library(readr)
#library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("correlations.csv", stringsAsFactors = FALSE)
full <- read.csv("full.csv", row.names=1, stringsAsFactors = FALSE) 
Turk <- read.csv("turk.csv", stringsAsFactors = FALSE)

@@

If all $K$ observers pick the same plot out of a lineup of twenty, we result in a p-value as small as $1/m^K$ . This research used $m= 20$, giving us a significance level (and Type 1 error rate) of $α = 0.05$. The plot of 'true' data is placed randomly amongst 19 null plots to form the lineup.
\begin{figure}[htbp]
  \centering
<<lineup.example, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE>>=
set.seed(1234)
a <- gen_true_data(24, 0.95)
td <- gather(a, variable, value, c(X1, X2))
b <- gen_null(24)
b$.n <- NULL
nd_l <- gather(b, variable, value, c(X1, X2))
nd_l$.n <- rep(1:19, rep(24, 19))
pos <- 7
td <- data.frame(.n=rep(pos, nrow(td)), td)
lg <- nd_l$.n < pos
nd_l1 <- data.frame(.n=nd_l$.n[lg], t=nd_l$t[lg], variable=nd_l$variable[lg], 
                    value=nd_l$value[lg])
nd_l2 <- data.frame(.n=nd_l$.n[!lg], t=nd_l$t[!lg], variable=nd_l$variable[!lg], 
                    value=nd_l$value[!lg])
nd_l2$.n <- nd_l2$.n + 1
d <- rbind(nd_l1, td, nd_l2)

plot <- ggplot(data=d, aes(x=t, y=value, colour=variable)) + geom_line() + facet_wrap(~.n, ncol=4, scales="free_y")  +
    theme_bw() + theme(axis.title.x = element_blank(),
                       axis.title.y = element_blank(),
                       axis.text.x = element_blank(),
                       axis.text.y = element_blank(),
                       axis.ticks = element_blank(),
                       legend.position="none")
print(plot)
@
  \caption{A lineup ($m = 20$) of line graphs. Which plot shows the series with the strongest correlation?}
  \label{lineup:example}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<designs, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE>>=
set.seed(101)
a <- gen_true_data(24, 0.95)
b <- gen_true_data(24, -0.95)
ca <- cor(a$X1, a$X2)
cb <- cor(b$X1, b$X2)
a_l <- gather(a, variable, value, -t)
b_l <- gather(b, variable, value, -t)
p1 <- ggplot(data=a_l, aes(x=t, y=value, colour=variable)) + geom_line() + labs(title="Overlaid line graph") +
      theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p2 <- ggplot(data=b_l, aes(x=t, y=value, colour=variable)) + geom_line() + labs(title="Overlaid line graph") +
      theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p3 <- ggplot(data=a, aes(x=X1, y=X2)) + geom_point() + labs(title="Scatterplot") +
      theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p4 <- ggplot(data=b, aes(x=X1, y=X2)) + geom_point() + labs(title="Scatterplot") +
      theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
grid.arrange(p1, p2, p3, p4, ncol=2)
@
  \label{designs}
  \caption{The same two data sets in both plot designs. t=24, correlation (left) = 0.946, correlation (right) = -0.943}
\end{figure}

@@

@@

\begin{figure}[htbp]
  \centering
<<powerdiff, dependson='results', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE>>=
Turk$correct <- Turk$percent*Turk$attempt
Turk$r <- round(Turk$correlation, 1)
Turk.line <- subset(Turk, test_param=="line")
Turk.scatter <- subset(Turk, test_param=="scatter")
Turk.line <- Turk.line[order(Turk.line$r, Turk.line$n, Turk.line$smoothed),c(10, 13, 16, 19, 20)]
Turk.line <- summarise(group_by(Turk.line, smoothed, n, r), sum(attempt), sum(correct))
Turk.scatter <- Turk.scatter[order(Turk.scatter$r, Turk.scatter$n, Turk.scatter$smoothed),c(10, 13, 16, 19, 20)]
Turk.scatter <- summarise(group_by(Turk.scatter, smoothed, n, r), sum(attempt), sum(correct))
colnames(Turk.scatter) <- c("smoothed", "n", "r", "s.attempt", "s.correct")
colnames(Turk.line) <- c("smoothed", "n", "r", "l.attempt", "l.correct")
prop <- cbind(Turk.line, Turk.scatter[4:5])
prop <- mutate(prop, l.adj = (l.correct+1)/(l.attempt+1), s.adj = (s.correct+1)/(s.attempt+1),
               df = s.attempt + l.attempt - 1, difference=s.adj-l.adj, t = qt(0.975, df),
               upper = difference + t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt),
               lower = difference - t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt))
ggplot(data=prop) + geom_line(aes(x=r, y=difference), colour="#99CC99", size=2) + 
                    geom_ribbon(aes(x=r, ymin=lower, ymax=upper), colour="#99CC99", fill="#99CC99", alpha=0.2) + 
                    labs(title="Difference in Power", x="Correlation") + facet_grid(n~smoothed)
@
 \label{powerdiff}
 \caption{Difference in estimated power to reveal the true plot by smoothness and sample size with a 95\% confidence interval. Values above zero indicate the scatter plot is more powerful than the overlaid line graph.}
\end{figure}

@@

Figure~\ref{samplesize} demonstrates the effects of changing sample size for unsmoothed data. The scatter plot has increased power to detect correlation almost universally for any increase. Sample size influences the overlaid lines differently, they appears to benefit for positively correlated true plots, but it does not improve the weak performance in negative correlation.
Figure~\ref{time} and Figure~\ref{confidence} give a breakdown of the interactions between the response variables: plot detection, time and confidence. Figure 8 is the histogram of the time taken to record a response, split by plot design and sign of correlation and true plot detection. The time data was highly positively skewed with a maximum of 1760 seconds so the variable was log-transformed. We found that the subject could identify the true plot out of the overlaid line graph 33.6\% of the time and it took on average $e^{3.442}$ = 31.2 seconds to make a choice. Successful detections were slightly faster than unsuccessful decision, taking on average 28.7 seconds to pick the true plot and 32.6 seconds if a null was selected. The scatter plots performed much better, with the true plot picked 52.9\% of the time, with an average of 22.7 seconds required to make a decision. If the true plot was detected it took only 18.6 seconds, and 29.3 seconds for a null plot selection.

@@

@@

\begin{figure}[htbp]
  \centering
<<confidence2, dependson='confidence', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)
y <- data.frame(table(full$subj_id))
keep2 <- y$Var1[y$Freq>9]
sub <- filter(full, subj_id %in% keep2)
sub <- select(sub, conf_level, correlation, test_param, smoothed, n, correct, sign, plot, subj_id) #c(7, 15, 16, 17, 20, 27)]
#sub <- summarise(group_by(sub, subj_id), correct = sum(correct), conf=mean(conf_level))
#sub <- merge(sub, y, by.x="subj_id", by.y="Var1")
#sub <- mutate(sub, prop = correct/Freq)
qplot(correlation, 6-conf_level, data=sub, alpha=I(0.1)) + 
  geom_smooth(method="loess") + 
  facet_grid(n~plot+smoothed) +
  labs(x = "Correlation", y = "Confidence (5=High, 1=Low)")
@
  \label{confidence2}
  \caption{Individual subject accuracy versus confidence. There does not appear to be any relationship between the two.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<pins, dependson='samplesize', fig.width=6, fig.height=10, out.width='0.7\\textwidth', echo=FALSE>>=
# correl <- read.csv("correlations.csv") # You have already read this
pin <- select(full, pic_id, response_0, actual_location, 
              test_param, smoothed, n) #full[,c(5, 6, 10, 15, 16, 17)]
# Need to use the tidyr commands instead of cSplit
# Here's where we will need to make some changes to incorporate the multiple picks
#pin <- pin %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
#pin$response_0 <- separate(pin, response_0, "response_0", sep=",", extra="drop")
pin$choice <- separate(pin, response_0, c("choice", "l1", "l2"), ",", extra="drop")$choice
pin$choice[str_detect(pin$actual_location, pin$response_0)] <- 
  pin$actual_location[str_detect(pin$actual_location, pin$response_0)]
                         #as.integer(pin$response_0)
counts <- data.frame(table(pin$pic_id, pin$choice))
counts$Var1 <- as.numeric(as.character(counts$Var1))
counts$Var2 <- as.numeric(as.character(counts$Var2))
colnames(counts) <- c("lineup", "plot", "count")
pin <- merge(counts, Turk, by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plot.x, count, smoothed, true_pos, n, test_param, r)#pin[,c(1, 2, 3, 12, 13, 15, 11, 20)]
pin$r <- factor(pin$r)
colnames(pin) <- c("lineup", "plot", "count", "smoothed", "true_pos", "n", "design", "r")
pin <- mutate(pin, design=ifelse(design=="scatter", "Scatterplot", "Overlaid Lines"))#, smoothed=ifelse(smoothed=="no", 0, 1))
pin$base <- 0
pin$Correlation <- diag(as.matrix(correl[pin$lineup, (pin$plot+2)]))
pin <- mutate(pin, true = ifelse(plot==true_pos, "True plot", "Null plot"))
pin <- merge(pin, Turk[,c(2, 16)], by.x = "lineup", by.y = "pic_id")
pin <- mutate(pin, percent = count/attempt)
ggplot(data=filter(pin, smoothed==0 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
       geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed() + facet_grid(n~r) + labs(title="Unsmoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed==1 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed==0 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Unsmoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
ggplot(data=subset(pin, smoothed==1 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
#Code to be fixed
@

@@

\section{Modelling Subject Responses}

@@

$$Power_{i} = \psi\left\{ \beta_{i,0} + \beta_{i,1} \cdot Correlation + \beta_{i,2}\cdot Sign + \beta_{i,3}\cdot Smoothed + \beta_{i,4}\cdot t + \beta_{i,5}\cdot Correlation \cdot Sign + \gamma_{i,1} \cdot subject_{j} \right\}$$

Where $\psi$ is the logit link function, $\psi(x) = \frac{e^{x}}{1+e^{x}}$, $r$ is the true plot correlation, Sign is the direction of the true plot correlation, $i$  is the plot design and $j$ is an observer specific random effect.

\begin{table}[htp]
\caption{Mixed Effects Logit Model for the predicted power of plot design. Sign = 1 if correlation > 0, 0 otherwise. Each plot design is estimated separately. Results must be transformed via the logit link function to generate a power prediction. Subjects with less than ten lineup evaluations were removed from the sample. Sample size for scatter plot model: 841, overlaid lines model: 843. The model is fitted using the lme4 package in R.}
\label{tab1}
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)

@@

#m8l <- glmer(correct.prop~offset(alpha) + rabs*rsgn + smoothed + n + (1|subj_id), data=filter(full.sub, plot == "L"), family="binomial", weights=attempts)
m8s <- glmer(correct.prop~offset(alpha) + rabs*rsgn + smoothed + n + (1|subj_id), data=filter(full.sub, plot == "S"), family="binomial", weights=attempts)
#pander(summary(m8l), justify=c('left', 'right', 'right', 'right', 'right', caption="Model fit for overlaid lines"))
#pander(summary(m8s)$coefficients, justify=c('left', 'right', 'right', 'right', 'right'), caption="Model fit for scatter plots")
#library(xtable)
kable(summary(m8s)$coefficients, format="latex")
@
\end{table}

@@

$$Power_{UR,s} = \psi\left\{ \beta_{s,0} + \beta_{s,1} \cdot |Correlation| + \beta_{s,2}\cdot Sign + \beta_{s,3}\cdot Smoothed + \beta_{s,4}\cdot t + \beta_{s,5}\cdot |Correlation| \cdot Sign + \gamma_{s,1} \cdot subject_{j} \right\}$$

@@

The restricted model is therefore:
$$Power_{R,s} = \psi\left\{ \beta_{s,0}+\beta_{s,1}\cdot |Correlation| + \beta_{s,3}\cdot Smoothed + \beta_{s,4}\cdot t +\gamma_{s,1} \cdot subject_{j} \right\}$$

@@

<<timefit, dependson='powerfit', echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ smoothed + r + n + rsgn*r + plot + plot*smoothed 
                  + plot*r + plot*n + plot*rsgn*r + plot*correct + (1|subj_id), data=full.sub)
pander(summary(timelmer), justify=c('left', 'right', 'right', 'right', 'right', caption="Model fit for time taken"))
@

>>>>

<<setup, echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
library(lme4)
library(ggplot2)
library(mnormt)
library(tidyr)
# Convert reshape2 to tidyr, melt to gather - done
#library(reshape2)
library(nullabor)
library(dplyr)
library(mFilter)
library(grid)
library(gridExtra)
library(stringr)
#library(pander)
#library(splitstackshape) - changed cSplit to unnest
#library(readr)
#library(lubridate)
# Convert these to read_csv at some point
correl <- read.csv("correlations.csv", stringsAsFactors = FALSE)
full <- read.csv("full.csv", row.names=1, stringsAsFactors = FALSE) 
Turk <- read.csv("turk.csv", stringsAsFactors = FALSE)

@@

If all $K$ observers pick the same plot out of a lineup of twenty, we result in a p-value as small as $1/m^K$ . This research used $m= 20$, giving us a significance level (and Type 1 error rate) of $α = 0.05$. The plot of 'true' data is placed randomly amongst 19 null plots to form the lineup.
\begin{figure}[htbp]
  \centering
<<lineup.example, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE>>=
set.seed(1234)
a <- gen_true_data(24, 0.95)
td <- gather(a, variable, value, c(X1, X2))
b <- gen_null(24)
nd_l <- gather(b, variable, value, c(X1, X2))
pos <- 7
td <- data.frame(.n=rep(pos, nrow(td)), td)
lg <- nd_l$.n < pos
nd_l1 <- data.frame(.n=nd_l$.n[lg], t=nd_l$t[lg], variable=nd_l$variable[lg], 
                    value=nd_l$value[lg])
nd_l2 <- data.frame(.n=nd_l$.n[!lg], t=nd_l$t[!lg], variable=nd_l$variable[!lg], 
                    value=nd_l$value[!lg])
nd_l2$.n <- nd_l2$.n + 1
d <- rbind(nd_l1, td, nd_l2)

ggplot(data=d, aes(x=t, y=value, colour=variable)) + geom_line() + facet_wrap(~.n, ncol=4, scales="free_y")  +
    theme_bw() + theme(axis.title.x = element_blank(),
                       axis.title.y = element_blank(),
                       axis.text.x = element_blank(),
                       axis.text.y = element_blank(),
                       axis.ticks = element_blank(),
                       legend.position="none")
@
  \caption{A lineup ($m = 20$) of line graphs. Which plot shows the series with the strongest correlation?}
  \label{lineup:example}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<designs, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE>>=
set.seed(101)
a <- gen_true_data(24, 0.95)
b <- gen_true_data(24, -0.95)
a_l <- gather(a, variable, value, -t)
b_l <- gather(b, variable, value, -t)
p1b <- ggplot(data=a_l, aes(x=t, y=value, colour=variable)) + geom_line() + labs(title="Overlaid line graph") +
      theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p2b <- ggplot(data=b_l, aes(x=t, y=value, colour=variable)) + geom_line() + labs(title="Overlaid line graph") +
      theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p3b <- ggplot(data=a, aes(x=X1, y=X2)) + geom_point() + labs(title="Scatterplot") +
      theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p4b <- ggplot(data=b, aes(x=X1, y=X2)) + geom_point() + labs(title="Scatterplot") +
      theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
grid.arrange(p1b, p2b, p3b, p4b, ncol=2)
@
  \label{designs}
  \caption{The same two data sets in both plot designs. t=24, correlation (left) = 0.946, correlation (right) = -0.943}
\end{figure}

@@

\subsection{Detection, Time and Confidence}

@@

\begin{figure}[htbp]
  \centering
<<powerdiff, dependson='results', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE>>=
Turk$correct <- Turk$percent*Turk$attempt
Turk$r <- round(Turk$correlation, 1)
#Turk.line <- subset(Turk, test_param=="line")
#Turk.scatter <- subset(Turk, test_param=="scatter")
prop <- Turk[order(Turk$r, Turk$n, Turk$smoothed),c("smoothed", "n", "attempt", "correct", "r", "plot")]
prop <- summarise(group_by(prop, smoothed, n, r), l.attempt=sum(ifelse(plot=="Overlaid Lines", attempt, 0)),
                                                  l.correct=sum(ifelse(plot=="Overlaid Lines", correct, 0)),
                                                  s.attempt=sum(ifelse(plot=="Scatterplot", attempt, 0)),
                                                  s.correct=sum(ifelse(plot=="Scatterplot", correct, 0)))
#Turk.line <- Turk.line[order(Turk.line$r, Turk.line$n, Turk.line$smoothed),c("smoothed", "n", "attempt", "correct", "r")]
#Turk.line <- summarise(group_by(Turk.line, smoothed, n, r, test_param), sum(attempt), sum(correct))
#Turk.scatter <- Turk.scatter[order(Turk.scatter$r, Turk.scatter$n, Turk.scatter$smoothed),c("smoothed", "n", "attempt", "correct", "r")]
#Turk.scatter <- summarise(group_by(Turk.scatter, smoothed, n, r), sum(attempt), sum(correct))
#colnames(Turk.scatter) <- c("smoothed", "n", "r", "s.attempt", "s.correct")
#colnames(Turk.line) <- c("smoothed", "n", "r", "l.attempt", "l.correct")
#prop <- cbind(Turk.line, Turk.scatter[4:5])
prop <- mutate(prop, l.adj = (l.correct+1)/(l.attempt+1), s.adj = (s.correct+1)/(s.attempt+1),
               df = s.attempt + l.attempt - 1, difference=s.adj-l.adj, t = qt(0.975, df),
               upper = difference + t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt),
               lower = difference - t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt))
ggplot(data=prop) + geom_errorbar(aes(x=r, ymax=upper, ymin=lower)) + geom_point(aes(x=r, y=difference)) +
        geom_hline(aes(yint=0, colour="red")) + labs(title="Difference in Power", x="Correlation", y="Scatterplot Advantage") + facet_grid(n~smoothed)
@
 \label{powerdiff}
 \caption{Difference in estimated power to reveal the true plot by smoothness and sample size with a 95\% confidence interval. Values above zero indicate the scatter plot is more powerful than the overlaid line graph.}
\end{figure}

@@

Figure~\ref{samplesize} demonstrates the effects of changing sample size for unsmoothed data. The scatter plot has increased power to detect correlation almost universally for any increase. Sample size influences the overlaid lines differently, they appears to benefit for positively correlated true plots, but it does not improve the weak performance in negative correlation.
Figure~\ref{time} and Figure~\ref{confidence} give a breakdown of the interactions between the response variables: plot detection, time and confidence. Figure~\ref{time} is the histogram of the time taken to record a response, split by plot design and sign of correlation and true plot detection. The time data was highly positively skewed with a maximum of 1760 seconds so the variable was log-transformed. We found that the subject could identify the true plot out of the overlaid line graph 33.6\% of the time and it took on average $e^{3.442}$ = 31.2 seconds to make a choice. Successful detections were slightly faster than unsuccessful decision, taking on average 28.7 seconds to pick the true plot and 32.6 seconds if a null was selected. The scatter plots performed much better, with the true plot picked 52.9\% of the time, with an average of 22.7 seconds required to make a decision. If the true plot was detected it took only 18.6 seconds, and 29.3 seconds for a null plot selection.

@@

\subsection{Selection Analysis}

@@

\begin{figure}[htbp]
  \centering
<<confidence2, dependson='time', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)
y <- data.frame(table(full$subj_id))
keep2 <- y$Var1[y$Freq>9]
sub <- filter(full, subj_id %in% keep2)
sub <- select(sub, conf_level, correlation, test_param, smoothed, n, correct, sign, plot, subj_id) #c(7, 15, 16, 17, 20, 27)]
#sub <- summarise(group_by(sub, subj_id), correct = sum(correct), conf=mean(conf_level))
#sub <- merge(sub, y, by.x="subj_id", by.y="Var1")
#sub <- mutate(sub, prop = correct/Freq)
qplot(correlation, 6-conf_level, data=sub, alpha=I(0.1)) + 
  geom_smooth(method="loess") + 
  facet_grid(n~plot+smoothed) +
  labs(x = "Correlation", y = "Confidence (5=High, 1=Low)")
@
  \label{confidence2}
  \caption{Individual subject accuracy versus confidence. There does not appear to be any relationship between the two.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<pins, dependson='samplesize', fig.width=6, fig.height=10, out.width='0.7\\textwidth', echo=FALSE>>=
# correl <- read.csv("correlations.csv") # You have already read this
count.setup <- select(full, pic_id, response_0, actual_location, 
              test_param, smoothed, n) #full[,c(5, 6, 10, 15, 16, 17)]
# Need to use the tidyr commands instead of cSplit
# Here's where we will need to make some changes to incorporate the multiple picks
#pin <- pin %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
#pin$response_0 <- separate(pin, response_0, "response_0", sep=",", extra="drop")
count.setup$choice <- separate(count.setup, response_0, c("choice", "l1", "l2"), ",", extra="drop")$choice
count.setup$choice[str_detect(count.setup$actual_location, count.setup$response_0)] <- 
  count.setup$actual_location[str_detect(count.setup$actual_location, count.setup$response_0)]
                         #as.integer(pin$response_0)
counts <- data.frame(table(count.setup$pic_id, count.setup$choice))
counts$Var1 <- as.numeric(as.character(counts$Var1))
counts$Var2 <- as.numeric(as.character(counts$Var2))
colnames(counts) <- c("lineup", "plot", "count")
pin <- merge(counts, Turk, by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plot.x, count, smoothed, true_pos, n, test_param, r)#pin[,c(1, 2, 3, 12, 13, 15, 11, 20)]
pin$r <- factor(pin$r)
colnames(pin) <- c("lineup", "plot", "count", "smoothed", "true_pos", "n", "design", "r")
pin <- mutate(pin, design=ifelse(design=="scatter", "Scatterplot", "Overlaid Lines"))#, smoothed=ifelse(smoothed=="no", 0, 1))
pin$base <- 0
pin$Correlation <- diag(as.matrix(correl[pin$lineup, (pin$plot+2)]))
pin <- mutate(pin, true = ifelse(plot==true_pos, "True plot", "Null plot"))
pin <- merge(pin, Turk[,c(2, 16)], by.x = "lineup", by.y = "pic_id")
pin <- mutate(pin, percent = count/attempt)
pin.a <- ggplot(data=filter(pin, smoothed==0 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
       geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed() + facet_grid(n~r) + labs(title="Unsmoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.b <- ggplot(data=subset(pin, smoothed==1 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.c <- ggplot(data=subset(pin, smoothed==0 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Unsmoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
pin.d <- ggplot(data=subset(pin, smoothed==1 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
grid.arrange(pin.a, pin.b, pin.c, pin.d, ncol=1)
@

@@

\subsection{Modelling Subject Responses}

@@

$$Power_{i} = \psi\left\{ \beta_{i,0} + \beta_{i,1} \cdot |\alpha| + \beta_{i,2}\cdot Sign + \beta_{i,3}\cdot Smoothed + \beta_{i,4}\cdot t + \beta_{i,5}\cdot |\alpha| \cdot Sign + \gamma_{i,1} \cdot subject_{j} \right\}$$

Where $\psi$ is the logit link function, $\psi(x) = \frac{e^{x}}{1+e^{x}}$, $\alpha$ is the true plot correlation, Sign is the direction of $\alpha$, $i$  is the plot design and $j$ is an observer specific random effect.

\begin{table}[htp]
\caption{Mixed Effects Logit Model for the predicted power of plot design. Sign = 1 if correlation > 0, 0 otherwise. Each plot design is estimated separately. Results must be transformed via the logit link function to generate a power prediction. Subjects with less than ten lineup evaluations were removed from the sample. Sample size for scatter plot model: 841, overlaid lines model: 843. The model is fitted using the lme4 package in R.}
\label{tab1}
\centering
<<powerfit, dependson='setup', results='asis', echo=FALSE, message=FALSE, error=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)

@@

m8l <- glmer(correct.prop~offset(alpha) + rabs*rsgn + smoothed + n + (1|subj_id), data=filter(full.sub, plot == "L"), family="binomial", weights=attempts)
m8s <- glmer(correct.prop~offset(alpha) + rabs*rsgn + smoothed + n + (1|subj_id), data=filter(full.sub, plot == "S"), family="binomial", weights=attempts)
#pander(summary(m8l), justify=c('left', 'right', 'right', 'right', 'right', caption="Model fit for overlaid lines"))
#pander(summary(m8s)$coefficients, justify=c('left', 'right', 'right', 'right', 'right'), caption="Model fit for scatter plots")
#library(xtable)
kable(summary(m8l)$coefficients, format="latex")
kable(summary(m8s)$coefficients, format="latex")
@
\end{table}

@@

$$Power_{UR,s} = \psi\left\{ \beta_{s,0} + \beta_{s,1} \cdot |\alpha| + \beta_{s,2}\cdot Sign + \beta_{s,3}\cdot Smoothed + \beta_{s,4}\cdot t + \beta_{s,5}\cdot |\alpha| \cdot Sign + \gamma_{s,1} \cdot subject_{j} \right\}$$

@@

The restricted model is therefore:
$$Power_{R,s} = \psi\left\{ \beta_{s,0}+\beta_{s,1}\cdot |\alpha| + \beta_{s,3}\cdot Smoothed + \beta_{s,4}\cdot t +\gamma_{s,1} \cdot subject_{j} \right\}$$

@@

<<timefit, dependson='powerfit', echo=FALSE, results='hide', message=FALSE, error=FALSE, warning=FALSE>>=
timelmer <-  lmer(log_time ~ smoothed + r + n + rsgn*r + plot + plot*smoothed 
                  + plot*r + plot*n + plot*rsgn*r + plot*correct + (1|subj_id), data=full.sub)
xable(summary(timelmer)$coefficients, format="latex")
@
